A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-09-23 main.tex
4.4 - note to self

LMM-Lasso-ggmix's poor performance in these scenarios are likely attributable to a number of a factors such as an ill-conditioned RRM  in $n \ge p$ settings \citep{ledoit2004well}. In addition, because LMM-Lasso-ggmix attempts to estimate more parameters than LMM-Lasso-Rakitsch, its optimization problem is not necessarily convex, making it prone to getting stuck in local minima before it is able to extensively explore the coefficient path. An examination of the number of iterations required for convergence for each $\lambda$ in the coefficient path suggests that this is the case for our various simulation settings \anna{Supplementary figure ? MAKE THIS AND MAKE IT PRETTY}. Getting stuck in this manner would lead to few iterations required for each $\lambda$ value before convergence, allowing for an advantage in terms of computational speed, but poor estimation, as we see in Figure \ref{fig:eta_beta_mse}.

\anna{See figure options: niter\_parLambda fig focusing on the eta = xi = 0.8 seting and displaying all data points - not just averages}

>>>>

LMM-Lasso-ggmix's poor performance in these scenarios are likely attributable to a number of a factors such as an ill-conditioned RRM  in $n \ge p$ settings \citep{ledoit2004well}. In addition, because LMM-Lasso-ggmix attempts to estimate more parameters than LMM-Lasso-Rakitsch, its optimization problem is not necessarily convex, making it prone to getting stuck in local minima before it is able to extensively explore the coefficient path. An examination of the number of iterations required for convergence for each $\lambda$ in the coefficient path suggests that this is the case for our various simulation settings \anna{Supplementary figure - in progress, stuck on dumb facet labeling issue}. Getting stuck in this manner would lead to few iterations required for each $\lambda$ value before convergence, allowing for an advantage in terms of computational speed, but poor estimation, as we see in Figure \ref{fig:eta_beta_mse}.
